Symmetric Peer-to-Peer Applications

### 2022-08-28 tpd-22.tex
...

\usepackage{xspace}
\newcommand{\FC}       {Freechains\xspace}
\newcommand{\reps}     {\emph{reps}\xspace}
\newcommand{\onerep}   {\emph{1~rep}\xspace}
\newcommand{\nreps}[1] {\emph{#1~reps\xspace}}
\newcommand{\code}[1]  {\texttt{\footnotesize{#1}}}
\newcommand{\Xon} {$1{\rightarrow}N$\xspace}
\newcommand{\Xno} {$1{\leftarrow}N$\xspace}
\newcommand{\Xnn} {$N{\leftrightarrow}N$\xspace}
\newcommand{\Xoo} {$1{\leftrightarrow}1$\xspace}
\newcommand{\Xo}  {$1{\hookleftarrow}$\xspace}

@@

\subsubsection{Application State}

@@

\subsubsection{Application Events}

@@

\subsubsection{Initialization Callback}

@@

\subsubsection{Simulation Callback}

@@

The middleware main loop \code{p2p\_loop} is responsible for calling the
application callbacks, and also controlling its timeline.
To achieve this, the loop continuously checks for network packets, local
inputs, and time ticks, as follows:

{\footnotesize
\begin{verbatim}
01  void p2p_loop (...,cb_ini,cb_sim,cb_ren,cb_evt) {
01    cb_ini(1);
01    cb_sim(<P2P_EVT_INIT>);
01
01    while (<app-running>) {
01      if (<next-packet>) {
01        // fast forward if too late
01        if (<packet-sync-time-future>) {
01          for (<step-by-step-sleep>) {
01            p2p_travel(<packet-sync-time>);
01            cb_ren();
01          }
01        }
01
01        if (<packet-evt>) {
01          if (<packet-evt-time-past>) {
01            for (<step-by-step-sleep>) {
01              p2p_travel(<packet-evt-time>);
01              cb_ren();
01            }
01            for (<step-by-step-sleep>) {
01              p2p_travel(<now>);
01              cb_ren();
01            }
01          } else {
01            cb_sim(<packet-evt>);
01            cb_eff();
01          }
01        }
01      }
01
01      if (<next-input>) {
01        p2p_evt evt;
01        if (cb_rec(&evt)) {
01          p2p_bcast(<future>, &evt);
01        }
01      }
01
01      if (<next-tick>) {
01        cb_sim(<P2P_EVT_TICK>);
01        <take-snapshot-every-XXXms>
01        cb_ren();
01      }
01    }
01
01    cb_ini(0);
01  }
\end{verbatim}
}

>>>>

\usepackage{xspace}
\newcommand{\FC}       {Freechains\xspace}
\newcommand{\reps}     {\emph{reps}\xspace}
\newcommand{\onerep}   {\emph{1~rep}\xspace}
\newcommand{\nreps}[1] {\emph{#1~reps\xspace}}
\newcommand{\code}[1]  {\texttt{\footnotesize{#1}}}
\newcommand{\Xon} {$1{\rightarrow}N$\xspace}
\newcommand{\Xno} {$1{\leftarrow}N$\xspace}
\newcommand{\Xnn} {$N{\leftrightarrow}N$\xspace}
\newcommand{\Xoo} {$1{\leftrightarrow}1$\xspace}
\newcommand{\Xo}  {$1{\hookleftarrow}$\xspace}
\newcommand{\lin}[1]{(\emph{ln. #1}\xspace)}

@@

\subsubsection{Application State}
\label{sec.tml.api.state}

@@

\subsubsection{Application Events}
\label{sec.tml.api.events}

@@

\subsubsection{Initialization Callback}
\label{sec.tml.api.cb_ini}

@@

\subsubsection{Simulation Callback}
\label{sec.tml.api.cb_sim}

@@

The middleware main loop \code{p2p\_loop} is responsible for calling the
application callbacks, and also controlling its timeline.
The loop continuously checks for network packets, local inputs, and time ticks,
as follows:

{\footnotesize
\begin{verbatim}
01  void p2p_loop (...,cb_ini,cb_sim,cb_ren,cb_evt) {
02    cb_ini(1);
03    cb_sim(<P2P_EVT_START>);
04
05    while (<app-running>) {
06      if (<next-packet>) {
07        // fast forward if I'm late
08        if (<packet-sync-future>) {
09          p2p_travel(<now>, <packet-sync-time>);
10        }
11
12        // travel back & forth if I'm early
13        if (<packet-evt-past>) {
14          p2p_travel(<now>, <packet-evt-time>);
15          p2p_travel(<packet-evt-time>, <now>);
16        }
17
18        // simulate in real time if I'm on time
19        if (<packet-evt-ok>) {
20          cb_sim(<packet-evt>);
21          cb_ren();
22        }
23      }
24
25      if (<next-input>) {
26        // broadcast event from local
27        p2p_evt evt;
28        if (cb_evt(&evt)) {
29          p2p_bcast(<future>, &evt);
30        }
31      }
32
33      // simulate tick in real time
34      if (<next-tick>) {
35        cb_sim(<P2P_EVT_TICK>);
36        <take-snapshot-every-second>
37        cb_ren();
38      }
39    }
40
41    cb_ini(0);
42  }
\end{verbatim}
}

The function receives the application callbacks as arguments \lin{1}
(Section~\ref{sec.tml.api}).
It first (and last) calls \code{cb\_ini} \lin{2,41} to initialize (and
finalize) the application.
Then, it calls \code{cb\_sim} \lin{3}, passing the event \code{START} to start
the application in real time
(Sections~\ref{sec.tml.api.events}~and~\ref{sec.tml.api.cb_sim}).
The main loop \lin{5--39} checks continuously for network packets \lin{6--23},
local input events \lin{25--31}, and time ticks \lin{33--38}.
%
If we receive a time synchronization packet \code{SYNC} from the future
\lin{7--10}, then the we fast forward the application to catch up in time
(Section~\ref{sec.tml}.b).
If we receive an event that should have been applied in the past \lin{12--16},
then we travel back and forth (Section~\ref{sec.tml}.a).
Otherwise, we just apply the event in real time \lin{18--22}
(Section~\ref{sec.tml.api.cb_sim}).

We detail the function \code{p2p\_travel} further

\subsubsection{The Time Machine}
\label{sec.tml.middleware.travel}
